Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Rahel's story uses the rhythm game, not Rahel.  Could be improved.
Temporarily comment out figure 2.

An older Rahel learns that the block language she used to talk with
the turtle is also used to write all the software running inside
her special book.  Rahel uses the blocks to write a new sort of rhythm
game.  Her younger brother has just received his own green book,
and Rahel writes him a story using her rhythm game to help him learn
to count.

@@

\begin{figure}
\centering
\epsfig{file=roger1.eps, height=1.5in} % width=3.2in
\caption{Diagram of Nell's primary interface.}\label{fig:nell}
\end{figure}

@@

>>>>

An older Rahel learns that the block language she used to talk with
the turtle is also used to write all the software running inside
her special book.  Rahel uses the blocks to write a new sort of rhythm
game.  Her younger brother has just received his own green book,
and Rahel writes him a story which uses her rhythm game to help him learn
to count.

@@

%\begin{figure}
%\centering
%\epsfig{file=roger1.eps, height=1.5in} % width=3.2in
%\caption{Diagram of Nell's primary interface.}\label{fig:nell}
%\end{figure}

@@

%Children learn in different ways...
